Research Review: \\The Extent of Adaptive Wild Introgression in Crops

### 2018-07-30 paper.tex
Update paper.tex
revised the Allaby 2015 sentence.

Beyond confounding detection of progenitor taxa, extensive introgression may necessitate a more nuanced view of crop origins.
In cases like maize and potato it is important to recognize the substantial contributions of introgressing taxa to modern crops.
While these crops may have originated from a single species or subspecies, the crops as we know them today have a broader genetic base.

>>>>

Beyond confounding detection of progenitor taxa, extensive introgression may necessitate a more nuanced view of crop origins.
In cases like maize and potato it is important to recognize the substantial contributions of introgressing taxa to modern crops.
While these crops may have originated from a single species or subspecies, the crops as we know them today have a broader genetic base.
%In addtion, the domestications of barley and rice might best be described as geographically noncentric due to the significant genetic contributions from wide-ranging locations \cite{allaby2015barley}.
The recognized contributions of multiple wild relatives and proto-domesticated crop varieties from across distant geographies into modern crops (which appears to be the case in barley and rice, for example) highlight the importance of polycentric and concentric conceptions of domestication \cite{allaby2015barley}.
